Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-06 longSC.tex
new figures with EKRT

\begin{figure*}[!]
            \begin{center}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig_SC_hydro_32.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig_SC_hydro_42.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig_SC_hydro_42.eps}}
              \end{center}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}. These SC(3,2) and SC(4,2) will be replaced with new figures for higher order correlations once we have the calculations from Harri Niemi et. al~\cite{Niemi:2015qia}.}
        \label{fig:Figure_5}
\end{figure*}

@@

\begin{figure}[p]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32.eps}}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42.eps}}
              \end{center}
             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.}
             \label{fig:Figure_8}
\end{figure}

>>>>

\begin{figure*}[!]
            \begin{center}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
              \end{center}
        \caption{Results of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The dashed lines are hydrodynamic predictions with various $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}. These SC(3,2) and SC(4,2) will be replaced with new figures for higher order correlations once we have the calculations from Harri Niemi et. al~\cite{Niemi:2015qia}.}
        \label{fig:Figure_5}
\end{figure*}

@@

\begin{figure}[p]
             \begin{center}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC32_EKRT.eps}}
              \resizebox{0.95\textwidth}{!}{\includegraphics{figs/fig5_QConly_xminpt_nSC42_EKRT.eps}}
              \end{center}
             \caption{NSC(3,2) (Top) and NSC(4,2) (Bottom) as a function of minimum $p_{\rm T}$ cuts in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to various AMPT models.}
             \label{fig:Figure_8}
\end{figure}
